Psyc 601 Multivariate Statistics Project

### 2013-08-15 writeups/proposal/proposal.tex
foo
Former-commit-id: 9c9e21f20d37118ce31bac2ecbfa9ed1beba0e48 [formerly 9a81e2b44301d2a888d32abe44338d1860a5e365]
Former-commit-id: 5dc9f89720a27f65430497e47c3af0aa0e41fc50

@@

@@

TODO: Natural question to ask is how can we build human-computer systems that help connect users to these hashtag information sources.

@@

TODO: Useful problem since real-time search on social media sites is growing \cite{Jansen2011}

@@

TODO: Summarize \cite{Rutledge2007}

>>>>

\usepackage[hyphens]{url}
%\usepackage{hyperref}
%\usepackage{breakurl}

@@

TODO: Useful problem since real-time search on social media sites is growing \cite{Jansen2011}
TODO: Users want to be quickly connected to the content that they care about, with minimal amount of searching necessary, since the amount of generated content on these sites is so vast.

TODO: Social media sites are composed almost entirely of human-generated content.
Users are searching through this content.

@@

TODO: Natural question to ask is if we can predict a users' interested hashtags, we have a better understanding of that user's goals on the site.
And with that understanding, we can improve their interaction with the site by tailoring the system to give them content that they care most about.

@@

@@

TODO: Summarize MALTA \cite{Rutledge2007}
